---
title: "Reproducible pitch"
author: "yihao"
date: "8/15/2020"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,message = FALSE)
```

## Reproducible pitch

This is for Course Project: Shiny Application and Reproducible Pitch. 

- Github repo please see: <https://yihaoy.shinyapps.io/ShinyApp/>.
- Shiny Application please see: <>.
- Reproducible Pitch please see: <>.

## Background
The experiment is based on `mtcars` dataset. According to R documentation, 

> It is a data frame with 32 observations on 11 (numeric) variables.\
[, 1]	mpg	Miles/(US) gallon\
[, 2]	cyl	Number of cylinders\
[, 3]	disp	Displacement (cu.in.)\
[, 4]	hp	Gross horsepower\
[, 5]	drat	Rear axle ratio\
[, 6]	wt	Weight (1000 lbs)\
[, 7]	qsec	1/4 mile time\
[, 8]	vs	Engine (0 = V-shaped, 1 = straight)\
[, 9]	am	Transmission (0 = automatic, 1 = manual)\
[,10]	gear	Number of forward gears\
[,11]	carb	Number of carburetors\

## mtcars dataset
```{r}
str(mtcars)
```



## example regression experiment

```{r}
require(ggplot2)
ggplot(data=mtcars,aes(wt,mpg))+geom_point()+geom_smooth(method='lm',aes(group=1))
```

